The paper on blockchain front-running

### 2018-09-24 frontrunning/Latex/sections/paper.tex
[frontrunning] Loopring polished

\subsubsection{Design Decision \#3: Dual Authoring\newline} % S 2 M: this is still vague, it requires better explanation.
Loopring is an open protocol proposed by Wang~\etal to build decentralized exchanges~\cite{wang2018loopring}. This protocol operates a hybrid model with off-chain order management and communication and merely the order matching takes place on the chain. To achieve high liquidity and price improvement, Loopring orders are grouped in \emph{ring orders}. After the required signatures are provided by a miner and owner of the order, see Figure~\ref{fig:vulnerable_loopring}, the ring miner sends the \emph{submitRing transaction} to the Loopring Smart Contract (LPSC) for verification and settlement. While the \emph{submitRing transaction} sits unconfirmed in the mempool, any front-runner can create a copy of this transaction with his address instead of the ring miner's address and then sign the hash of the ring using his own private key. By paying a higher gasPrice, block miners choose the front-runner's transaction instead of the original \emph{submitRing transaction}. However, in the new version of Loopring protocol, this issue is resolves using the \emph{dual-authoring} scheme. This solution sets two levels of authorization for orders - one for settlement, and one for order matching. As it can be seen in Figure~\ref{fig:not_vulnerable_loopring}, each owner of an order generates a pair of public key (auth-address) and private key (auth-key), which are different from his address and its corresponding private key. These auth-keys are used to sign the hash of the ring and will further prevent anyone from regenerating the same \emph{submitRing transaction}. The reason is that the auth-keys are only known to the miner of the ring as they are not part of the on-chain transaction. Doing so, it is assured that (i) the orders are not modified (because they are signed by the owner), (ii) no other miner can mine the ring (because the miner's address is signed by the initial miner), and no user can front-run the \emph{submitRing transaction} (because other users do not have access to the auth-keys and hence are not able to generate new transactions with auth-keys signatures on them).

% S 2 M: Also I'm not sure about the figures. they do not add enough clarity to the text.

>>>>

\subsubsection{Design Decision \#3: Dual Authoring\newline} Loopring is an open protocol proposed by Wang~\etal to build decentralized exchanges~\cite{wang2018loopring}. This protocol operates a hybrid model with off-chain order management and communication while only the order matching takes place on the chain. In this protocol, the orders are grouped in \emph{ring orders} immediately after they are sent by the users. Next, the required signatures are provided by a miner and owner of the order, see Figure~\ref{fig:vulnerable_loopring}. Eventually, the ring miner sends the \emph{submitRing transaction} to the Loopring Smart Contract (LPSC) for verification and settlement. While the \emph{submitRing transaction} sits unconfirmed in the mempool, any front-runner can create a copy of this transaction with his address instead of the ring miner's address and then sign the hash of the ring using his own private key. By paying a higher gasPrice, block miners choose the front-runner's transaction instead of the original \emph{submitRing transaction}. 
To solve this issue, the new version of Loopring protocol uses the \emph{dual-authoring} scheme. This solution sets two levels of authorization for orders - one for settlement, and one for order matching. As it can be seen in Figure~\ref{fig:not_vulnerable_loopring}, each owner of an order generates a pair of public key (auth-address) and private key (auth-key), which are different from his address and its corresponding private key. These auth-keys are used to sign the hash of the ring and will further prevent anyone from regenerating the same \emph{submitRing transaction}. The reason is that the auth-keys are only known to the miner of the ring as they are not part of the on-chain transaction. Doing so, it is assured that (i) the orders are not modified (because they are signed by the owner), (ii) no other miner can mine the ring (because the miner's address is signed by the initial miner), and no user can front-run the \emph{submitRing transaction} (because other users do not have access to the auth-keys and hence are not able to generate new transactions with auth-keys signatures on them).
